\fontfamily{phv}\selectfont{Research A Proposal}

### 2013-09-24 docs/proposal/doc.tex
begin BCCD gemaakt

\subsection*{Brain connectivity}
\subsubsection*{Functional connectivity}
The functional connectivity describes the statistical dependance of neuronal activity of different brain regions \cite{friston1993functional}.
This gives an insight in the organization of the brain, even though the exact functioning is still unclear \cite{Lowe2000, doria2010, Bullmore2009}.
Functional connectivity is strongly time-dependant, as these dependancies may be short-lasting.

@@

\subsection*{Causal discovery methods}
% ...

@@

The causal discovery method which we will use is the PC-algorithm (spirtes, 2000). An advantage of this algorithm is that the scaling is relatively well.

>>>>

\subsection*{Brain connectivity}
\subsubsection*{Functional connectivity}
The functional connectivity describes the statistical dependance of neuronal activity of different brain regions \cite{friston1993functional}.
This gives an insight in the organization of the brain, even though the exact functioning is still unclear.
Functional connectivity is strongly time-dependant, as these dependancies may be short-lasting.
The functional connectivity can be deduced from resting-state networks \cite{Lowe2000, doria2010, Bullmore2009}.

@@

\subsection*{Causal discovery methods}
The causal discovery method which we will use is the BCCD-algorithm. This algorithm finds both the structure of a network as well as the direction of the connections of this network. An advantage of this algorithm is that the scaling is relatively good. BCCD also finds probabilities of connections.

@@
